### 2009-05-18 doc/tutorials/ws-programming-tutorial/doc/tex_sec_echoservice/sec_echoservice.tex
These are also not executables

Listing~\ref{lst:sececho_service_cpp} contains the source code of the Secure Echo Web Service. As one can see, the only difference, compared to the source code of the previous section, is the additional code to process the \textit{SecHandler} starting at line~\ref{lst_code:sececho_service_cpp_process_secH}. Obviously only the incoming queue is processed and in case the \textit{SecHandler} fails, the SOAP service returns a fault message. The file, which is revealing a lot more information, is the server configuration file which is shown in Listing~\ref{lst:sececho_server_configuration_file_xml}. 
To enable \textit{SecHandlers} to work with identities, it is almost essential to utilise the TLS layer.
% Fixed IP are also possible but not recommended..
The TLS layer extracts the identity such that it later can be used to process the \textit{SecHandler}.
In line~\ref{lst_code:arched_sec_conffile_plugins} and line~\ref{lst_code:arched_sec_conffile_plugins2} two additional plugins 
are named to be loaded which are implementing of the \textit{SecHandlers} and \textit{PDPs}.
%
%  FIRST ONE
%
The first \textit{SecHandler} is declared at line~\ref{lst_code:arched_sec_conffile_secH2}. 
The PDP \textit{allow.pdp} always returns a positive result, such that everyone who passes the \textit{SecHandler} is mapped to the user \textit{nobody}. 
%
% SECOND ONE
%
The second \textit{SecHandler} limits the access to the SOAP services using the \textit{arc.authz} \textit{SecHandler} and the \textit{simplelist} policy, see line~\ref{lst_code:arched_sec_conffile_secH1}. A similar example was already shown in Listing~\ref{lst:sec_service_component_xml}. The \textit{simplelist} policy returns a positive result if the identity of the certificate corresponds to an identity within the file \textit{clientlist.txt}. A small example of such a file is displayed in Listing~\ref{lst:simplelist_example}.
\lstsetCPP
\lstinputlisting
	[
	label=lst:sececho_service_cpp,
	caption={[Source code of the Secure Echo Service.]
	\textbf{Source code of the Secure Echo Service.}}
	]
{../src/services/secechoservice/secechoservice.cpp}
%
%
The first part of an entry needs to be the distinguished name (DN) of the current client. A DN is a string which represents a user uniquely and is created using the identity of the certificate. To get the correct DN of a client one can use the TLS Echo Web Service and check the log-file. The second part of an entry specifies the user the identity shall be mapped to. In the present case, the identity will be mapped to \textit{griduser}. In case the policy is unable to match the identity, the PDP returns a negativ result.
The \textit{SecHandler} within the SOAP component limits the access of SOAP to a certain group of users.
%
%
% The third ONE
The last \textit{SecHandler}, used in the server configuration file, is to be seen starting with line~\ref{lst_code:arched_sec_conffile_secH3}. The \textit{SecHandler} is chosen to be \textit{arc.authz} which leads to the fact that the access to the Echo Web Service will be limited one more time to a subset of the group. The policy \textit{arc.pdp} returns a positive result in case the rules encapsulated within the file \textit{policy.xml} will return a positive result.\\
\lstsetARCHEDXML
\lstinputlisting
	[
	label=lst:sececho_server_configuration_file_xml, float=htb
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/services/secechoservice/arched_sec_echoservice.xml}

@@

Within the sample policy, which was shown in Listing~\ref{lst:sececho_policy_xml}, three different examples of rule states are prepared: PERMIT, INDETERMINATE and NOT APPLICABLE.
The first rule, starting at line~\ref{lst_code:policy.xml_rule1}, is fitting to the server configuration file such that a user with a suitable identity will produce the state PERMIT. 
Since there is no rule within the policy which will have the DENY state, in particular no rule that could have matched earlier, this rule lets the client pass the PDP.
The second rule begins after line~\ref{lst_code:policy.xml_rule2}. It is arranged in a manner such that the state INDETERMINATE will be induced. Two things are checked within it: the identity based on authentication method Shibboleth\footnote{Shibboleth is an open-source implementation for authentication and authorization based on the XML standard SAML (Security Assertion Markup Language).} 
and the path of the requested HTTP URL. Due to the fact, that the HTTP path is fitting to the requested one, but the authentication was not done by Shibboleth, the rule is not able to decide for a DENY or a PERMIT state --- the rule produces an INDETERMINATE state.
The last rule is defined in line~\ref{lst_code:policy.xml_rule3}. It is constructed such that is permits the access to the HTTP method GET. 
One can see, that within the server configuration file the Web Service uses the method POST. If a client wants to access the Service and reaches the PDP, a couple of requests are generated which are describing the manner the client wants to access the serivice. Some of these request will concern the HTTP method GET. In these cases, the rule returns NOT APPLICABLE. In the cases where the requests for a HTTP method is missing (i.e. in the request which only concerns the SOAP access) the state of the rule will be INDETERMINATE.\\
\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:sececho_policy_xml, float=htb,
	caption={[Policy file for the \textit{arc.pdp} policy decision point.]
	\textbf{Policy file for the \textit{arc.pdp} policy decision point.}}
	]
{../src/services/secechoservice/policy_example.xml}

>>>>

Listing~\ref{lst:sececho_service_cpp} contains the source code of the Secure Echo Web Service. As one can see, the only difference, compared to the source code of the previous section, is the additional code to process the \textit{SecHandler} starting at line~\ref{lst_code:sececho_service_cpp_process_secH}. Obviously only the incoming queue is processed and in case the \textit{SecHandler} fails, the SOAP service returns a fault message. The file, which is revealing a lot more information, is the server configuration file which is shown in Listing~\ref{lst:sececho_server_configuration_file_xml}. 
To enable \textit{SecHandlers} to work with identities, it is almost essential to utilise the TLS layer.
% Fixed IP are also possible but not recommended..
The TLS layer extracts the identity such that it later can be used to process the \textit{SecHandler}.
In line~\ref{lst_code:arched_sec_conffile_plugins} and line~\ref{lst_code:arched_sec_conffile_plugins2} two additional plugins 
are named to be loaded which are implementing of the \textit{SecHandlers} and \textit{PDPs}.
%
%  FIRST ONE
%
The first \textit{SecHandler} is declared at line~\ref{lst_code:arched_sec_conffile_secH2}. 
The PDP \textit{allow.pdp} always returns a positive result, such that everyone who passes the \textit{SecHandler} is mapped to the user \textit{nobody}. 
%
% SECOND ONE
%
The second \textit{SecHandler} limits the access to the SOAP services using the \textit{arc.authz} \textit{SecHandler} and the \textit{simplelist} policy, see line~\ref{lst_code:arched_sec_conffile_secH1}. A similar example was already shown in Listing~\ref{lst:sec_service_component_xml}. The \textit{simplelist} policy returns a positive result if the identity of the certificate corresponds to an identity within the file \textit{clientlist.txt}. A small example of such a file is displayed in Listing~\ref{lst:simplelist_example}.
\lstsetCPP
\lstinputlisting
	[
	label=lst:sececho_service_cpp,
	caption={[Source code of the Secure Echo Service.]
	\textbf{Source code of the Secure Echo Service.}}
	]
{../examples/src/services/secechoservice/secechoservice.cpp}
%
%
The first part of an entry needs to be the distinguished name (DN) of the current client. A DN is a string which represents a user uniquely and is created using the identity of the certificate. To get the correct DN of a client one can use the TLS Echo Web Service and check the log-file. The second part of an entry specifies the user the identity shall be mapped to. In the present case, the identity will be mapped to \textit{griduser}. In case the policy is unable to match the identity, the PDP returns a negativ result.
The \textit{SecHandler} within the SOAP component limits the access of SOAP to a certain group of users.
%
%
% The third ONE
The last \textit{SecHandler}, used in the server configuration file, is to be seen starting with line~\ref{lst_code:arched_sec_conffile_secH3}. The \textit{SecHandler} is chosen to be \textit{arc.authz} which leads to the fact that the access to the Echo Web Service will be limited one more time to a subset of the group. The policy \textit{arc.pdp} returns a positive result in case the rules encapsulated within the file \textit{policy.xml} will return a positive result.\\
\lstsetARCHEDXML
\lstinputlisting
	[
	label=lst:sececho_server_configuration_file_xml, float=htb
	caption={[HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the Arc intern echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../examples/src/services/secechoservice/arched_sec_echoservice.xml}

@@

Within the sample policy, which was shown in Listing~\ref{lst:sececho_policy_xml}, three different examples of rule states are prepared: PERMIT, INDETERMINATE and NOT APPLICABLE.
The first rule, starting at line~\ref{lst_code:policy.xml_rule1}, is fitting to the server configuration file such that a user with a suitable identity will produce the state PERMIT. 
Since there is no rule within the policy which will have the DENY state, in particular no rule that could have matched earlier, this rule lets the client pass the PDP.
The second rule begins after line~\ref{lst_code:policy.xml_rule2}. It is arranged in a manner such that the state INDETERMINATE will be induced. Two things are checked within it: the identity based on authentication method Shibboleth\footnote{Shibboleth is an open-source implementation for authentication and authorization based on the XML standard SAML (Security Assertion Markup Language).} 
and the path of the requested HTTP URL. Due to the fact, that the HTTP path is fitting to the requested one, but the authentication was not done by Shibboleth, the rule is not able to decide for a DENY or a PERMIT state --- the rule produces an INDETERMINATE state.
The last rule is defined in line~\ref{lst_code:policy.xml_rule3}. It is constructed such that is permits the access to the HTTP method GET. 
One can see, that within the server configuration file the Web Service uses the method POST. If a client wants to access the Service and reaches the PDP, a couple of requests are generated which are describing the manner the client wants to access the serivice. Some of these request will concern the HTTP method GET. In these cases, the rule returns NOT APPLICABLE. In the cases where the requests for a HTTP method is missing (i.e. in the request which only concerns the SOAP access) the state of the rule will be INDETERMINATE.\\
\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:sececho_policy_xml, float=htb,
	caption={[Policy file for the \textit{arc.pdp} policy decision point.]
	\textbf{Policy file for the \textit{arc.pdp} policy decision point.}}
	]
{../examples/src/services/secechoservice/policy_example.xml}
